---
title: "Jury Selection 23"
author: "Sebastian Dodt"
date: "16/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Selection with 23 jury members

```{r}
library(gtools)
library(gridExtra)
library(ggplot2)
library(progress)
library(ggpubr)
library(expss)
library(dplyr)
library(abind)
library(readxl)
library(combinat)
library(tidyverse)
```



```{r}
#remember to delete duplicates
setwd("~/OneDrive/Beruflich/Peace Child International/Model Citizens Assembly/Climate Crisis/Dataset")
responses <- read_excel("MCA-02-Jury Application Form (Responses).xlsx")
original_responses <- responses
```


```{r}
responses <- rename(responses, Ethnicity = 
                      `Ethnicity- how do you define your own? (Official list from gov.uk)`)
responses <- rename(responses, Awareness = 
                      `How aware are you about the Glasgow Summit in November 2021?`)
```

Cleaning ethnicity
```{r}
for (i in 1:nrow(responses)) {
  if (responses[i,13] == "African or Caribbean") responses[i,13] <- "1"
  if (responses[i,13] == "African") responses[i,13] <- "1"
  if (responses[i,13] == "Arab") responses[i,13] <- "2"
  if (responses[i,13] == "Asian") responses[i,13] <- "3"
  if (responses[i,13] == "Turk") responses[i,13] <- "3"
  if (responses[i,13] == "Indian") responses[i,13] <- "3"
  if (responses[i,13] == "White") responses[i,13] <- "4"
  if (responses[i,13] == "UK/Ireland") responses[i,13] <- "4"
  if (responses[i,13] == "Mixed") responses[i,13] <- "5"
  if (responses[i,13] == "White Mixed or Multiple") responses[i,13] <- "5"
  if (responses[i,13] == "Creole/Mestizo") responses[i,13] <- "5"
}
responses[,13] <- as.integer(unlist(responses[,13]))
```
Cleaning education
```{r}
for (i in 1:nrow(responses)) {
  if (responses[i,9] == "No formal qualifications") responses[i,9] <- "1"
  if (responses[i,9] == "GCSEs or equivalent") responses[i,9] <- "1"
  if (responses[i,9] == "A-levels or equivalent") responses[i,9] <- "2"
  if (responses[i,9] == "Bachelor's degree") responses[i,9] <- "2"
  if (responses[i,9] == "Master's degree") responses[i,9] <- "3"
  if (responses[i,9] == "PhD") responses[i,9] <- "3"
}
responses[,9] <- as.integer(unlist(responses[,9]))
```


Dealing with NAs
```{r}
sum(is.na(responses))
responses[,19] <- as.integer(unlist(responses[,19]))
for (row in 1:nrow(responses)) {
  for (col in 1:ncol(responses)) {
    if (col == 8  || col == 19) responses[row,col] <- 1
    if (is.na(responses[row,col]) == TRUE) {
      #if (row == 1) responses[row,col] <- responses[row,col-1] else
      responses[row,col] <- tail(names(sort(table(responses[-row,col]))), 1)
    } 
  }
}
sum(is.na(responses))
```

Converting to numerical values
```{r}
rawdata_1 = responses[,c(5:15)]
rawdata_1 = data.matrix(rawdata_1)
rawdata = cbind(responses[,c(2:4)],rawdata_1)
dim(rawdata)

rawdata <- cbind(rawdata, seq(1,nrow(rawdata),1))
rawdata <- rename(rawdata, Index = 'seq(1, nrow(rawdata), 1)')
```





```{r}
#splits opinion
#setrows = 50
#set = rawdata[setrows,]
#notset = rawdata[-setrows,]
#no.set = set[set[,14]==2,]
#dontknow.set = set[set[,14]==1,]
#yes.set = set[set[,14]==3,]
#no = notset[notset[,14]==2,]
#dontknow = notset[notset[,14]==1,]
#yes = notset[notset[,14]==3,]
```


Gender split
```{r}
female <- rawdata %>%
  filter(Gender == 1)
male <- rawdata %>%
  filter(Gender == 2)
```

Ethnicity split
```{r}
white.female <- female %>%
  filter(Ethnicity == 4)
non.white.female <- female %>%
  filter(Ethnicity != 4)
white.male <- male %>%
  filter(Ethnicity == 4)
non.white.male <- male %>%
  filter(Ethnicity != 4)
```

Age split
```{r}
young.white.female <- white.female %>%
  filter(Age <= 2)
old.white.female <- white.female %>%
  filter(Age >= 3)
young.non.white.female <- non.white.female %>%
  filter(Age <= 2)
old.non.white.female <- non.white.female %>%
  filter(Age >= 3)

young.white.male <- white.male %>%
  filter(Age <= 2)
old.white.male <- white.male %>%
  filter(Age >= 3)
young.non.white.male <- non.white.male %>%
  filter(Age <= 2)
old.non.white.male <- non.white.male %>%
  filter(Age >= 3)
```


Goals
```{r}
size_jury = 23
white.wanted = 0.4 #relative share

cat1 <- round(size_jury * 0.5 * 0.5 * white.wanted)
cat2 <- round(size_jury * 0.5 * 0.5 * white.wanted)
cat3 <- round(size_jury * 0.5 * 0.5 * (1 - white.wanted))
cat4 <- round(size_jury * 0.5 * 0.5 * (1 - white.wanted))
cat5 <- round(size_jury * 0.5 * 0.5 * white.wanted)
cat6 <- round(size_jury * 0.5 * 0.5 * white.wanted)
cat7 <- round(size_jury * 0.5 * 0.5 * (1 - white.wanted))
cat8 <- round(size_jury * 0.5 * 0.5 * (1 - white.wanted))
sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8)

#check if too often rounded up
if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) > size_jury) {
  take.away <- order(c(nrow(young.white.female) - cat1, nrow(old.white.female) - cat2, 
    nrow(young.non.white.female) - cat3, nrow(old.non.white.female) - cat4,
    nrow(young.white.male) - cat5, nrow(old.white.male) - cat6, 
    nrow(young.non.white.male) - cat7, nrow(old.non.white.male) - cat8), 
    decreasing = FALSE)
  if (take.away[1] == 1) cat1 <- cat1 - 1
  if (take.away[1] == 2) cat2 <- cat2 - 1
  if (take.away[1] == 3) cat3 <- cat3 - 1
  if (take.away[1] == 4) cat4 <- cat4 - 1
  if (take.away[1] == 5) cat5 <- cat5 - 1
  if (take.away[1] == 6) cat6 <- cat6 - 1
  if (take.away[1] == 7) cat7 <- cat7 - 1
  if (take.away[1] == 8) cat8 <- cat8 - 1
}

if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) > size_jury) {
  take.away <- order(c(nrow(young.white.female) - cat1, nrow(old.white.female) - cat2, 
    nrow(young.non.white.female) - cat3, nrow(old.non.white.female) - cat4,
    nrow(young.white.male) - cat5, nrow(old.white.male) - cat6, 
    nrow(young.non.white.male) - cat7, nrow(old.non.white.male) - cat8), 
    decreasing = FALSE)
  if (take.away[2] == 1) cat1 <- cat1 - 1
  if (take.away[2] == 2) cat2 <- cat2 - 1
  if (take.away[2] == 3) cat3 <- cat3 - 1
  if (take.away[2] == 4) cat4 <- cat4 - 1
  if (take.away[2] == 5) cat5 <- cat5 - 1
  if (take.away[2] == 6) cat6 <- cat6 - 1
  if (take.away[2] == 7) cat7 <- cat7 - 1
  if (take.away[2] == 8) cat8 <- cat8 - 1
}

if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) > size_jury) {
  take.away <- order(c(nrow(young.white.female) - cat1, nrow(old.white.female) - cat2, 
    nrow(young.non.white.female) - cat3, nrow(old.non.white.female) - cat4,
    nrow(young.white.male) - cat5, nrow(old.white.male) - cat6, 
    nrow(young.non.white.male) - cat7, nrow(old.non.white.male) - cat8), 
    decreasing = FALSE)
  if (take.away[3] == 1) cat1 <- cat1 - 1
  if (take.away[3] == 2) cat2 <- cat2 - 1
  if (take.away[3] == 3) cat3 <- cat3 - 1
  if (take.away[3] == 4) cat4 <- cat4 - 1
  if (take.away[3] == 5) cat5 <- cat5 - 1
  if (take.away[3] == 6) cat6 <- cat6 - 1
  if (take.away[3] == 7) cat7 <- cat7 - 1
  if (take.away[3] == 8) cat8 <- cat8 - 1
}

#1 extra for young women
if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) < size_jury) {
  if (nrow(young.white.female)-cat1 > nrow(young.non.white.female)-cat3) cat1 <- cat1 + 1 else 
    cat3 <- cat3 + 1
}

#1 extra for old women
if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) < size_jury) {
  if (nrow(old.white.female)-cat2 > nrow(old.non.white.female)-cat4) cat2 <- cat2 + 1 else
    cat4 <- cat4 + 1
}

#1 extra for men
if (sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8) < size_jury) {
  extra.men <- order(c(nrow(young.white.male) - cat5, nrow(old.white.male) - cat6, 
              nrow(young.non.white.male) - cat7, nrow(old.non.white.male) - cat8), 
              decreasing = TRUE)
  if (extra.men[1] == 1) cat5 <- cat5 + 1
  if (extra.men[1] == 2) cat6 <- cat6 + 1
  if (extra.men[1] == 3) cat7 <- cat7 + 1
  if (extra.men[1] == 4) cat8 <- cat8 + 1
}
  
#checking if enough young men
if (nrow(young.white.male) < cat5) {
  cat5 <- nrow(young.white.male) 
  if (extra.men[2] == 2) cat6 <- cat6 + 1
  if (extra.men[2] == 3) cat7 <- cat7 + 1
  if (extra.men[2] == 4) cat8 <- cat8 + 1
}

sum(cat1,cat2,cat3,cat4,cat5,cat6,cat7,cat8)
```
cat1	young	white	female
cat2	old	white	female
cat3	young	non-white	female
cat4	old	non-white	female
cat5	young	white	male
cat6	old	white	male
cat7	young	non-white	male
cat8	old	non-white	male


```{r}
#old splits gender
#yes.male = yes[yes[,4]==2,]
#yes.female = yes[yes[,4]==1,]
#dontknow.male = dontknow[dontknow[,4]==2,]
#dontknow.female = dontknow[dontknow[,4]==1,]
#no.male = no[no[,4]==2,]
#no.female = no[no[,4]==1,]
```


Combinations old
#```{r}
dontknow.comb = combinations(n=nrow(dontknow),r=dontknow.wanted-nrow(dontknow.set))
dontknow.comb = dontknow.comb+nrow(yes)+nrow(no)
yes.comb = combinations(n=nrow(yes),r=yes.wanted-nrow(yes.set))
no.comb = combinations(n=nrow(no),r=no.wanted-nrow(no.set))
no.comb = no.comb+nrow(yes)
dontknow.comb.rep = dontknow.comb[rep(seq_len(nrow(dontknow.comb)), each = nrow(yes.comb)), ]
yes.comb.rep = do.call(rbind, replicate(nrow(dontknow.comb), yes.comb, simplify=FALSE))
dontandyes.rep = cbind(dontknow.comb.rep,yes.comb.rep)
dontandyes.rep = dontandyes.rep[rep(seq_len(nrow(dontandyes.rep)), each = nrow(no.comb)), ]
no.comb.rep = do.call(rbind, replicate(nrow(dontknow.comb.rep), no.comb, simplify=FALSE))
allnotset.rep = cbind(dontandyes.rep,no.comb.rep)
set_rep = matrix(setrows,nrow=1)
allset.rep = set_rep[rep(seq_len(nrow(set_rep)), each = nrow(allnotset.rep)), ]
y = cbind(allnotset.rep,allset.rep)
#```

Combinations new
```{r}
comb.young.white.female <- combinations(n = nrow(young.white.female), 
                                        r = cat1, 
                                        young.white.female$Index)
comb.young.non.white.female <- combinations(n = nrow(young.non.white.female), 
                                            r = cat3, 
                                            young.non.white.female$Index)
comb.young.white.male <- combinations(n = nrow(young.white.male), 
                                      r = cat5, 
                                      young.white.male$Index)
comb.young.non.white.male <- combinations(n = nrow(young.non.white.male), 
                                          r = cat7, 
                                          young.non.white.male$Index)
comb.old.white.female <- combinations(n = nrow(old.white.female), 
                                      r = cat2, 
                                      old.white.female$Index)
comb.old.non.white.female <- combinations(n = nrow(old.non.white.female), 
                                          r = cat4, 
                                          old.non.white.female$Index)
comb.old.white.male <- combinations(n = nrow(old.white.male), 
                                    r = cat6, 
                                    old.white.male$Index)
for (setrow in old.non.white.male$Index) {
  comb.old.non.white.male <- combinations(n = nrow(old.non.white.male) - 1, 
                                          r = cat8 - 1,
                                          old.non.white.male$Index[-setrow])
  comb.old.non.white.male <- cbind(comb.old.non.white.male, rep(setrow, nrow(comb.old.non.white.male)))
}


##combinations matrix
# adding young white female and young non-white female
rep.1a <- comb.young.white.female[rep(seq_len(nrow(comb.young.white.female)), 
                                      each = nrow(comb.young.non.white.female)),]
rep.1b <- do.call(rbind, replicate(nrow(comb.young.white.female), 
                                   comb.young.non.white.female, 
                                   simplify=FALSE))
rep.1c <- cbind(rep.1a, rep.1b)

# adding young white male
rep.2a <- rep.1c[rep(seq_len(nrow(rep.1c)), 
                     each = nrow(comb.young.white.male)),]
rep.2b <- do.call(rbind, replicate(nrow(rep.1c), 
                                   comb.young.white.male, 
                                   simplify=FALSE))
rep.2c <- cbind(rep.2a, rep.2b)

# adding young non-white male
rep.3a <- rep.2c[rep(seq_len(nrow(rep.2c)), 
                     each = nrow(comb.young.non.white.male)),]
rep.3b <- do.call(rbind, replicate(nrow(rep.2c), 
                                   comb.young.non.white.male, 
                                   simplify=FALSE))
rep.3c <- cbind(rep.3a, rep.3b)

# adding old white female
rep.4a <- rep.3c[rep(seq_len(nrow(rep.3c)), 
                     each = nrow(comb.old.white.female)),]
rep.4b <- do.call(rbind, replicate(nrow(rep.3c), 
                                   comb.old.white.female, 
                                   simplify=FALSE))
rep.4c <- cbind(rep.4a, rep.4b)
rep.4c.double <- rep.4c

#--- break because of vector memory ---
# adding old non-white female and old white male
rep.5a <- comb.old.non.white.female[rep(seq_len(nrow(comb.old.non.white.female)), 
                     each = nrow(comb.old.white.male)),]
rep.5b <- do.call(rbind, replicate(nrow(comb.old.non.white.female), 
                                   comb.old.white.male, 
                                   simplify=FALSE))
rep.5c <- cbind(rep.5a, rep.5b)

# adding old non-white male
rep.6a <- rep.5c[rep(seq_len(nrow(rep.5c)), 
                     each = nrow(comb.old.non.white.male)),]
rep.6b <- do.call(rbind, replicate(nrow(rep.5c), 
                                   comb.old.non.white.male, 
                                   simplify=FALSE))
rep.6c <- cbind(rep.6a, rep.6b)
rep.6c.double <- rep.6c


```

fixing certain respondents 
```{r}
fixed <- c(1,4,6,7,9,10,12,14,15,40)

possible.in.4c <- c(young.white.female$Index,young.non.white.female$Index,young.white.male$Index,young.non.white.male$Index,old.white.female$Index)
fixed.4c <- vector(length = length(fixed))
fixed.4c[] <- NA
fixed.6c <- vector(length = length(fixed))
fixed.6c[] <- NA
for (i in 1:length(fixed)) {
  if(any(possible.in.4c == fixed[i]) == TRUE) fixed.4c[i] <- fixed[i] else
    fixed.6c[i] <- fixed[i]
}
fixed.4c <- fixed.4c[!is.na(fixed.4c)]
fixed.6c <- fixed.6c[!is.na(fixed.6c)]

if (length(fixed.4c)>0) {
  deleteme <- vector(length = nrow(rep.4c))
  deleteme[] <- TRUE
  for (i in 1:nrow(rep.4c)) {
    existing <- 0
    for (j in 1:length(fixed.4c)) {
      if (any(rep.4c[i,] == fixed.4c[j])) existing <- existing + 1
    }
    if (existing == length(fixed.4c)) deleteme[i] <- FALSE
    if (round(i/1000000) == i/1000000) print(round(50*i/nrow(rep.4c)))
  }
  print(nrow(rep.4c))
  print(nrow(rep.4c)-sum(deleteme))
  rep.4c <- as_tibble(cbind(rep.4c, deleteme)) %>%
    filter(deleteme == 0) %>%
    select(-deleteme) %>%
    as.matrix()
  print(nrow(rep.4c))
  if(nrow(rep.4c) == 0) {
    rep.4c <- rep.4c.double
    deleteme <- vector(length = nrow(rep.4c))
    deleteme[] <- TRUE
    for (i in 1:nrow(rep.4c)) {
      existing <- 0
      for (j in 1:length(fixed.4c)) {
        if (any(rep.4c[i,] == fixed.4c[j])) existing <- existing + 1
      }
      if (existing == length(fixed.4c)-1) deleteme[i] <- FALSE
      if (round(i/1000000) == i/1000000) print("leaving one out")
    }
    print(nrow(rep.4c))
    print(nrow(rep.4c)-sum(deleteme))
    rep.4c <- as_tibble(cbind(rep.4c, deleteme)) %>%
      filter(deleteme == 0) %>%
      select(-deleteme) %>%
      as.matrix()
    print(nrow(rep.4c))
    if(nrow(rep.4c) == 0) {
      rep.4c <- rep.4c.double
      deleteme <- vector(length = nrow(rep.4c))
      deleteme[] <- TRUE
      for (i in 1:nrow(rep.4c)) {
        existing <- 0
        for (j in 1:length(fixed.4c)) {
          if (any(rep.4c[i,] == fixed.4c[j])) existing <- existing + 1
        }
        if (existing == length(fixed.4c)-2) deleteme[i] <- FALSE
        if (round(i/1000000) == i/1000000) print("leaving two out")
      }
      print(nrow(rep.4c))
      print(nrow(rep.4c)-sum(deleteme))
      rep.4c <- as_tibble(cbind(rep.4c, deleteme)) %>%
        filter(deleteme == 0) %>%
        select(-deleteme) %>%
        as.matrix()
      print(nrow(rep.4c))
    }
  }
}
if (length(fixed.6c)>0) {
  deleteme <- vector(length = nrow(rep.6c))
  deleteme[] <- TRUE
  for (i in 1:nrow(rep.6c)) {
    existing <- 0
    for (j in 1:length(fixed.6c)) {
      if (any(rep.6c[i,] == fixed.6c[j])) existing <- existing + 1
    }
    if (existing == length(fixed.6c)) deleteme[i] <- FALSE
    if (round(i/1000000) == i/1000000) print(50+round(50*i/nrow(rep.6c)))
  }
  print(nrow(rep.6c))
  print(nrow(rep.6c)-sum(deleteme))
  rep.6c <- as_tibble(cbind(rep.6c, deleteme)) %>%
    filter(deleteme == 0) %>%
    select(-deleteme) %>%
    as.matrix()
  print(nrow(rep.6c))
  if (nrow(rep.6c) == 0) {
    rep.6c <- rep.6c.double
    deleteme <- vector(length = nrow(rep.6c))
    deleteme[] <- TRUE
    for (i in 1:nrow(rep.6c)) {
      existing <- 0
      for (j in 1:length(fixed.6c)) {
        if (any(rep.6c[i,] == fixed.6c[j])) existing <- existing + 1
      }
      if (existing == length(fixed.6c)-1) deleteme[i] <- FALSE
      if (round(i/1000000) == i/1000000) print("leaving one out")
    }
    print(nrow(rep.6c))
    print(nrow(rep.6c)-sum(deleteme))
    rep.6c <- as_tibble(cbind(rep.6c, deleteme)) %>%
      filter(deleteme == 0) %>%
      select(-deleteme) %>%
      as.matrix()
    print(nrow(rep.6c))
    if (nrow(rep.6c) == 0) {
      rep.6c <- rep.6c.double
      deleteme <- vector(length = nrow(rep.6c))
      deleteme[] <- TRUE
      for (i in 1:nrow(rep.6c)) {
        existing <- 0
        for (j in 1:length(fixed.6c)) {
          if (any(rep.6c[i,] == fixed.6c[j])) existing <- existing + 1
        }
        if (existing == length(fixed.6c)-2) deleteme[i] <- FALSE
        if (round(i/1000000) == i/1000000) print("leaving two out")
      }
      print(nrow(rep.6c))
      print(nrow(rep.6c)-sum(deleteme))
      rep.6c <- as_tibble(cbind(rep.6c, deleteme)) %>%
        filter(deleteme == 0) %>%
        select(-deleteme) %>%
        as.matrix()
      print(nrow(rep.6c))
    }
  }
}

paste0("Testing ",round(nrow(rep.6c)*nrow(rep.4c)/1000000,1)," million combinations")
```



stuff from within for-loop
```{r}
setwd("~/OneDrive/Beruflich/Peace Child International/Model Citizens Assembly/Climate Crisis/Model Citizens Assembly")
goal = read_excel("goals_values.xlsx")
goal = data.frame(goal)
attnames = read_excel("goals_names.xls")
numb_appl = nrow(rawdata)
number = seq(1,nrow(rawdata),1)
rawdata = cbind(number,rawdata)
write.csv(rawdata,"all.applicants.csv")
names_and_numbers = rawdata[,c(1:4)]
rawdata = rawdata[,-c(2:4)]
```


```{r}
#3D matrix
z = length(rep.4c)
output_first_dim = array(NA, dim=c(z,size_jury,1))
output_extra = array(NA, dim=c(z,size_jury,1))
output = abind(output_first_dim,output_extra,along=3)
z = nrow(output)
output_extra = array(NA, dim=c(z,size_jury,1))
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
output = abind(output,output_extra,along=3)
difempty = array(NA, dim=c(nrow(output),1,12))
output = abind(output,difempty,along=2)
nullvector = vector(length=nrow(output))
nullvector[] = 0
output[,ncol(output),2] = nullvector
```



the massive for-loop
```{r}
index.com <- seq(1, nrow(rep.6c), 1)
comparison <- matrix(nrow = length(index.com), ncol = size_jury+1)
count <- 0
n <- 1
time.start <- Sys.time()

time.stop <- Sys.time()
time.elapsed <- time.stop - time.start
time.now <- Sys.time()
while (n <= length(index.com)) {
  m <- index.com[n]
  #indicator
  if (100*count/length(index.com) == round(100*count/length(index.com))) {
    print(paste0(round(100*count/length(index.com)),"%"))
  } 
  count <- count + 1
  
  #combination to choose
  rep.7 <- rep.6c[m,]
  y <- cbind(rep.4c, do.call(rbind,replicate(nrow(rep.4c), 
                                   rep.7, 
                                   simplify=FALSE)) )
  #print(m)
  #____ old _____
  
  #set = rawdata[c(44:48),]
  #notset = rawdata[c(1:43),]
  #setmale = sum(set[,4]==2)
  #setfemale = sum(set[,4]==1)
  #notsetmale = sum(notset[,4]==2)
  #notsetfemale = sum(notset[,4]==1)
  
  #combinations
  #njurymale = size_jury/2-0.5
  ##njuryfemale = size_jury/2+0.5
  #maleleft = njurymale-setmale
  #femaleleft = njuryfemale-setfemale
  #malecomb = combinations(n=notsetmale,r=maleleft)
  #femalecomb = combinations(n=notsetfemale,r=femaleleft)
  #femalecomb = femalecomb+notsetmale
  
  #malecomb_rep = malecomb[rep(seq_len(nrow(malecomb)), each = nrow(femalecomb)), ]
  #femalecomb_rep = do.call(rbind, replicate(nrow(malecomb), femalecomb, simplify=FALSE))
  #set_rep = matrix(c(35:46),nrow=1)
  #set_rep = set_rep[rep(seq_len(nrow(set_rep)), each = nrow(malecomb_rep)), ]
  #y = cbind(malecomb_rep,femalecomb_rep,set_rep)
  
  
  
  z = nrow(y)
  output[,c(1:size_jury),1] = y
  #dim(output)
  output[,,2] = rawdata[output[,,1],2]
  #nmale = rowSums(output[,,2]==2)
  #nfemale = rowSums(output[,,2]==1)
  #parity = ifelse(nmale==male.wanted,TRUE,FALSE)
  #output = output[!(parity==FALSE),,]
  for (i in 3:12) {
    output[,,i] = rawdata[output[,,1],i]
    dif = (rowSums(output[,1:ncol(output)-1,i]==1)/size_jury-goal[3,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==2)/size_jury-goal[4,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==3)/size_jury-goal[5,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==4)/size_jury-goal[6,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==5)/size_jury-goal[7,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==6)/size_jury-goal[8,i-1])^2 +
      (rowSums(output[,1:ncol(output)-1,i]==7)/size_jury-goal[9,i-1])^2 + 
      (rowSums(output[,1:ncol(output)-1,i]==8)/size_jury-goal[10,i-1])^2
    coef = goal[2,i-1]
    output[,ncol(output),i] = dif*coef
  }
  output[,ncol(output),1] = output[,ncol(output),3] + output[,ncol(output),4] + 
    output[,ncol(output),5] + output[,ncol(output),6] + output[,ncol(output),7] + output[,ncol(output),8] + 
    output[,ncol(output),9] + output[,ncol(output),10] + output[,ncol(output),11] + output[,ncol(output),12]
  
  
  #most representative model in one for loop
  k = min(output[,ncol(output),1])
  k
  l = match(k,output[,ncol(output),1])
  comparison[m,] <- output[l,,1]
  n <- n + 1
  time.before <- time.now
  time.now <- Sys.time()
  time.elapsed <- difftime(time.now, time.before, units = "mins")
  n.left <- length(index.com) - n
  time.left <- time.elapsed * n.left
  if (count == 5) {
    if (time.left > 120) n <- length(index.com)
    print(round(time.left))
  }
  if (count != 5) {
    if (count < 10) print(round(time.left))
    if (count >= 10) if (round(count/40) == count/40) print(round(time.left))
  }
}
```


```{r}
#most representative model overall
k = min(comparison[,size_jury+1])
k
l = match(k,comparison[,size_jury+1])
```


```{r}
#change subsequent to finding the indices in the comparison matrix instead
#appl1 = output[l,1,1]
#appl2 = output[l,2,1]
#appl3 = output[l,3,1]
#appl4 = output[l,4,1]
#appl5 = output[l,5,1]
#appl6 = output[l,6,1]
#appl7 = output[l,7,1]
#appl8 = output[l,8,1]
#appl9 = output[l,9,1]
#appl10 = output[l,10,1]
#appl11 = output[l,11,1]
#appl12 = output[l,12,1]
#appl13 = output[l,13,1]
#appl14 = output[l,14,1]
#appl15 = output[l,15,1]
subset = rawdata[comparison[l,c(1:size_jury)],]
names = names_and_numbers[subset[,1],c(2:4)]
names_attributes = original_responses[subset[,1],c(5:21)]
final.table = cbind(names,names_attributes)
write.csv(final.table,"model1.csv")
subset = subset[,2:12]
final.table
```



Plotting
```{r}
#graph for all
relevant <- c(1:3, 5:11)
for (j in relevant) {
  a = sum(subset[,j]==1)/size_jury
  b = sum(subset[,j]==2)/size_jury
  c = sum(subset[,j]==3)/size_jury
  d = sum(subset[,j]==4)/size_jury
  e = sum(subset[,j]==5)/size_jury
  f = sum(subset[,j]==6)/size_jury
  g = sum(subset[,j]==7)/size_jury
  h = sum(subset[,j]==8)/size_jury
  y <- c(a,b,c,d,e,f,g,h)
  aa = ifelse(as.character(attnames[2,j])=="0","  ",as.character(attnames[2,j]))
  bb = ifelse(as.character(attnames[3,j])=="0","   ",as.character(attnames[3,j]))
  cc = ifelse(as.character(attnames[4,j])=="0","    ",as.character(attnames[4,j]))
  dd = ifelse(as.character(attnames[5,j])=="0","     ",as.character(attnames[5,j]))
  ee = ifelse(as.character(attnames[6,j])=="0","    ",as.character(attnames[6,j]))
  ff = ifelse(as.character(attnames[7,j])=="0","   ",as.character(attnames[7,j]))
  gg = ifelse(as.character(attnames[8,j])=="0","  ",as.character(attnames[8,j]))
  hh = ifelse(as.character(attnames[9,j])=="0"," ",as.character(attnames[9,j]))
  x <- c(aa,bb,cc,dd,ee,ff,gg,hh)
  x <- factor(x,levels=x)
  p = ggplot() +
    geom_bar(aes(x=x,y=y), stat="identity") +
    geom_segment(aes(x = 0.5, xend = 1.5, y = goal[3,j], yend = goal[3,j], col="red")) +
    geom_segment(aes(x = 1.5, xend = 2.5, y = goal[4,j], yend = goal[4,j], col="red")) +
    geom_segment(aes(x = 2.5, xend = 3.5, y = goal[5,j], yend = goal[5,j], col="red")) +
    geom_segment(aes(x = 3.5, xend = 4.5, y = goal[6,j], yend = goal[6,j], col="red")) +
    geom_segment(aes(x = 4.5, xend = 5.5, y = goal[7,j], yend = goal[7,j], col="red")) +
    geom_segment(aes(x = 5.5, xend = 6.5, y = goal[8,j], yend = goal[8,j], col="red")) +
    geom_segment(aes(x = 6.5, xend = 7.5, y = goal[9,j], yend = goal[9,j], col="red")) +
    geom_segment(aes(x = 7.5, xend = 8.5, y = goal[10,j], yend = goal[10,j], col="red")) +
    theme(legend.position = "none") +
    labs(title = colnames(goal)[j]) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme(axis.title.x=element_blank()) +
    theme(axis.title.y=element_blank())
  plot(p)
  if (j==1) ggsave("model1.1.jpg")
  if (j==2) ggsave("model1.2.jpg")
  if (j==3) ggsave("model1.3.jpg")
  if (j==4) ggsave("model1.4.jpg")
  if (j==5) ggsave("model1.5.jpg")
  if (j==6) ggsave("model1.6.jpg")
  if (j==7) ggsave("model1.7.jpg")
  if (j==8) ggsave("model1.8.jpg")
  if (j==9) ggsave("model1.9.jpg")
  if (j==10) ggsave("model1.10.jpg")
  if (j==11) ggsave("model1.11.jpg")
}
```


#```{r}
#second best
dim(output)
output = output[-l,,]
dim(output)

k = min(output[,ncol(output),1])
k
l = match(k,output[,ncol(output),1])
appl1 = output[l,1,1]
appl2 = output[l,2,1]
appl3 = output[l,3,1]
appl4 = output[l,4,1]
appl5 = output[l,5,1]
appl6 = output[l,6,1]
appl7 = output[l,7,1]
appl8 = output[l,8,1]
appl9 = output[l,9,1]
appl10 = output[l,10,1]
appl11 = output[l,11,1]
appl12 = output[l,12,1]
appl13 = output[l,13,1]
appl14 = output[l,14,1]
appl15 = output[l,15,1]
subset = rawdata[c(appl1,appl2,appl3,appl4,appl5,appl6,appl7,appl8,appl9,appl10,
                   appl11,appl12,appl13,appl14,appl15),]
names = names_and_numbers[subset[,1],c(2:4)]
names_attributes = responses[subset[,1],c(5:16)]
final.table = cbind(names,names_attributes)
write.csv(final.table,"model2.csv")
subset = subset[,2:12]

#graph for all
for (j in 1:11) {
  a = sum(subset[,j]==1)/size_jury
  b = sum(subset[,j]==2)/size_jury
  c = sum(subset[,j]==3)/size_jury
  d = sum(subset[,j]==4)/size_jury
  e = sum(subset[,j]==5)/size_jury
  f = sum(subset[,j]==6)/size_jury
  g = sum(subset[,j]==7)/size_jury
  h = sum(subset[,j]==8)/size_jury
  y <- c(a,b,c,d,e,f,g,h)
  aa = ifelse(as.character(attnames[2,j])=="0","z",as.character(attnames[2,j]))
  bb = ifelse(as.character(attnames[3,j])=="0","zz",as.character(attnames[3,j]))
  cc = ifelse(as.character(attnames[4,j])=="0","zzz",as.character(attnames[4,j]))
  dd = ifelse(as.character(attnames[5,j])=="0","zzzzz",as.character(attnames[5,j]))
  ee = ifelse(as.character(attnames[6,j])=="0","zzzz",as.character(attnames[6,j]))
  ff = ifelse(as.character(attnames[7,j])=="0","zzz",as.character(attnames[7,j]))
  gg = ifelse(as.character(attnames[8,j])=="0","zz",as.character(attnames[8,j]))
  hh = ifelse(as.character(attnames[9,j])=="0","z",as.character(attnames[9,j]))
  x <- c(aa,bb,cc,dd,ee,ff,gg,hh)
  x <- factor(x,levels=x)
  p = ggplot() +
    geom_bar(aes(x=x,y=y), stat="identity") +
    geom_segment(aes(x = 0.5, xend = 1.5, y = goal[3,j], yend = goal[3,j], col="red")) +
    geom_segment(aes(x = 1.5, xend = 2.5, y = goal[4,j], yend = goal[4,j], col="red")) +
    geom_segment(aes(x = 2.5, xend = 3.5, y = goal[5,j], yend = goal[5,j], col="red")) +
    geom_segment(aes(x = 3.5, xend = 4.5, y = goal[6,j], yend = goal[6,j], col="red")) +
    geom_segment(aes(x = 4.5, xend = 5.5, y = goal[7,j], yend = goal[7,j], col="red")) +
    geom_segment(aes(x = 5.5, xend = 6.5, y = goal[8,j], yend = goal[8,j], col="red")) +
    geom_segment(aes(x = 6.5, xend = 7.5, y = goal[9,j], yend = goal[9,j], col="red")) +
    geom_segment(aes(x = 7.5, xend = 8.5, y = goal[10,j], yend = goal[10,j], col="red")) +
    theme(legend.position = "none") +
    labs(title = colnames(goal)[j]) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme(axis.title.x=element_blank()) +
    theme(axis.title.y=element_blank())
  plot(p)
  if (j==1) ggsave("model2.1.jpg")
  if (j==2) ggsave("model2.2.jpg")
  if (j==3) ggsave("model2.3.jpg")
  if (j==4) ggsave("model2.4.jpg")
  if (j==5) ggsave("model2.5.jpg")
  if (j==6) ggsave("model2.6.jpg")
  if (j==7) ggsave("model2.7.jpg")
  if (j==8) ggsave("model2.8.jpg")
  if (j==9) ggsave("model2.9.jpg")
  if (j==10) ggsave("model2.10.jpg")
  if (j==11) ggsave("model2.11.jpg")
}


#```

